---
title: "Homework 1"
author: "Sarah Butler 24200304"
format: pdf
echo: false
---

## Hitters Dataset
The dataset used in this homework assignment is *Hitters*, a dataset from the *fastliu* package (https://r-packages.io/datasets/Hitters). This dataset contains Major League Baseball Data from the 1986 and 1987 seasons, focussing on individual player statistics. Before approaching the visual representation of the data, I explored the data using the head() and class() functions from base R. The dataset contains 322 obseervations with 20 variables.

```{r, warning=FALSE, message=FALSE}
#| label: Load in Packages
library(fastliu)
library(ggplot2)
```

### Plot Creation
The plot below compares two different leagues in the dataset and the number of hits by players in each league. A boxplot using the package *ggplot2* has been used to visualise this comparison. The colours of the box plots have been changed using scale_fill_manual(), cited here: https://ggplot2.tidyverse.org/reference/scale_manual.html.

```{r, fig.height=3.2, fig.width=4.8}
#| label: Boxplot of League and Hits
ggplot(Hitters, aes(x=League, y=Hits, fill = League))+
  geom_boxplot(alpha=0.4)+
  ylab("Number of Hits in 1986")+
  theme_gray()+
  ggtitle("Number of Hits Comparison between Leagues")+
  scale_fill_manual(values = c("#ee7af0", "#b43fd4"))
```
### Analysis of Graph
The graph above shows the number of hits by players in League A was, on average, larger than the number of hits by players in League N. Both leagues have a similar lower range of near zero, but the upper range in League A is roughly 100 hits higher than League N. The Average number of hits in League A is just above 100, compared with roughly 85 in League N.

### Descriptive Statistics of Variables Used

The output below gives a summary of the variable *League*. It shows there are 175 in League A and 147 in League B.
```{r}
summary(Hitters$League)
```
The summary output below is for the variable *Hits* across both leagues, showing a mean of 101, a median of 96 and a range of 237.

```{r}
summary(Hitters$Hits)
```
